deckard: A Declarative Tool for Machine Learning Robustness Evaluations

### 2025-12-08 paper.tex
edits after review

Various versions of this software have been used in multiple published and forthcoming works by the author of \texttt{deckard}. 
While this paper does not present new experimental results—its focus is the software system itself—all of these prior studies have been made fully reproducible using the example pipelines included in the \texttt{examples} directory of the source repository (\url{https://github.com/simplymathematics/deckard}
). 
One such published work, now reproducible via \texttt{examples/attack_defence_survey}, provides a large survey of attacks and defenses against canonical datasets and models (C. Meyers, Löfstedt, and Elmroth 2023). 
A subsequent study examined the run-time requirements of various attacks before and after model retraining (reproducible via \texttt{examples/retraining}) (Charles Meyers et al. 2024). 
Another work formalized a method for estimating a model’s time-to-failure under a suite of attacks and introduced a metric comparing attack cost to training cost (reproducible via \texttt{examples/survival_heuristic}) (Meyers et al. 2023). 
Additionally, an unpublished study uses this time-to-failure framework to analyse the cost-efficiency of different hardware choices when facing adversarial workloads (reproducible via \texttt{examples/power}) (C. Meyers et al. 2024). 
Finally, another project leveraged the tooling to train a client-side model using compression-based distance measures for text (reproducible via \texttt{examples/compression}).

>>>>

Various versions of this software have been used in multiple published and forthcoming works by the author of \texttt{deckard}. 
While this paper does not present new experimental results—its focus is the software system itself—all of these prior studies have been made fully reproducible using the example pipelines included in the \texttt{examples} directory of the source repository (\href{https://github.com/simplymathematics/deckard}{https://github.com/simplymathematics/deckard}
). 
One such published work, now reproducible via \texttt{examples/attack\_defence\_survey}, provides a large survey of attacks and defenses against canonical datasets and models (C. Meyers, Löfstedt, and Elmroth 2023). 
A subsequent study examined the run-time requirements of various attacks before and after model retraining (reproducible via \texttt{examples/retraining}) (Charles Meyers et al. 2024). 
Another work formalized a method for estimating a model’s time-to-failure under a suite of attacks and introduced a metric comparing attack cost to training cost (reproducible via \texttt{examples/survival\_heuristic}) (Meyers et al. 2023). 
Additionally, an unpublished study uses this time-to-failure framework to analyse the cost-efficiency of different hardware choices when facing adversarial workloads (reproducible via \texttt{examples/power}) (C. Meyers et al. 2024). 
Finally, another project leveraged the tooling to train a client-side model using compression-based distance measures for text (reproducible via \texttt{examples/compression}).
